%-------------------------
% Resume in Latex
% Author : Reece Kalmar
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Reece Kalmar} \\ \vspace{1pt}
    \small 801-971-7163 $|$ \href{mailto:x@x.com}{\underline{ralmarkalmar@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/reece-kalmar/}{\underline{https://www.linkedin.com/in/reece-kalmar/}} $|$
    \href{https://github.com/ReeceKalmar}{\underline{https://github.com/ReeceKalmar}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Utah}{Salt Lake City, UT}
      {Bachelor's of Science in Computer Science}{Aug. 2022 -- Dec 2025}
    \resumeSubheading
      {Salt Lake Community College}{Salt Lake City, UT}
      {Associate of Science}{Aug. 2021 -- May 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {NFL Data Science Research}{Jan 2024 -- May 2024}
      {University of Utah}{SLC, UT}
      \resumeItemListStart
        \resumeItem{Developed visualizations for  NFL data using Python libraries such as Pandas, Matplotlib, NumPy, Seaborn, Plotly and machine learning tools like Scikit-learn}
        \resumeItem{Cleaned and analyzed NFL playoff data, implementing a machine learning model that had a prediction accuracy of 90\%.}
        \resumeItem{Applied different statistical models, including Bernoulli distributions, linear regression, K-Means, to understand the underlying dataset.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineer Intern}{May 2023 -- September 2023}
      {Spa Wellness Center}{Draper, UT}
      \resumeItemListStart
        \resumeItem{Integrated Aesthetic Record EMR with Growth99 and Mailchimp using Zapier to automate data flow and improve aesthetician productivity by 33\%.}
        \resumeItem{Developed and integretared REST API using Java Spring Boot to interface with NoSQL data base.}
        \resumeItem{Used the same API to chart clients business habits and purchases to better improve product offerings.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Spreadsheet} $|$ \emph{C\#, MStest, Blazor, Javascript}}{Aug 2024 -- September 2024}
          \resumeItemListStart
            \resumeItem{Developed a spreadsheet web app, using blazor and javascript to create a dynamic web app cabaple of resizing a users spreadsheet to their liking.}
            \resumeItem{Implemented algorithm for parsing and evaluating infix formulas and cell dependencies.}
            \resumeItem{Used json to enable the user to save and load different spreadsheets.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Snake} $|$ \emph{C\#, Blazor, Javascript, HTML, CSS}}{September 2024 -- December 2024}
          \resumeItemListStart
            \resumeItem{Developed a multiplayer Snake game, using networking via TCP and sockets, SQL, and json to send and recieve game state.}
            \resumeItem{Implemented game logic and collision detection serverside to reduce computing required user side. The game controller (server) sends game state regularly for high fps (144fps).}
            \resumeItem{Used SQL database with the backend server to store gamestate during set event that would store player scores game stateetc. This enabled the collection how a game played out}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{LoLAPIWrapper} $|$ \emph{TypeScript, Expressjs, Docker, Python, AWS, PostgreSQL }}{November 2024 -- Current}
          \resumeItemListStart
            \resumeItem{Developed a RESTful api that interacts and acts as an interface with various different endpoints from Riot games.}
            \resumeItem{Used with Python to collect mass amount of player data later to be used in a machine learning model. Was able to collect 300,000 player acount information}
            \resumeItem{Project was dockerized to run on AWS ec2 instance, in conjuction with a python script which enabled the automatic pulling of data from the api and storing it in an Amazon RDS PostgreSQL database. }
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C\#, NoSQL, JavaScript/TypeScript, HTML/CSS} \\
     \textbf{Frameworks}{: ExpressJs, JUnit, MSTest, Tailwind CSS, SpringBoot, Winston, ASP.NET} \\
     \textbf{Developer Tools}{: Nodejs, Git, VS Code, Bash, Maven, Dotnet, Docker, AWS, SQL, NextJS} \\
     \textbf{Libraries}{: React, pandas, NumPy, Matplotlib, Seaborn, Plotly, Scikit-learn}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
